Estimating Output Loss due to being Unrecognized as States

### 2019-03-02 paper/paper.tex
Revise the number of countries dropped from the sample #28 #40
2 more countries are dropped as they do not have real GDP observations for all years from 1992-2013, as found out by #28
Add the total number of countries in the base sample #40 #28

\subsection{Country boundaries}
To aggregate nighttime light intensity at the 30 arc-second cell level into the country level, we need the spatial data on country boundaries. 
We use GADM (2018), following Alesina et al.\ (2016) and Dreher et al.\ (2015) among others. 
The data include 256 countries and overseas territories. 
One country, Vatican, is dropped from the sample because it is smaller than the 30 arc-second cell. 
In addition, 73 countries and territories are also dropped from the sample as real GDP data is unavailable.

\section{Methodology}
% Model of real GDP
We model real GDP in territory $i$ in year $t$, denoted by $y_{it}$, as follows:
\begin{equation}\label{gdp}
\ln(y_{it}) = \beta \ln(L_{it}) + \mu_i + \eta_t + \varepsilon_{it},
\end{equation}
where $L_{it}$ is nighttime light intensity in territory $i$ in year $t$, $\mu_i$ the territory fixed effect, $\eta_t$ the year fixed effect, and $\varepsilon_{it}$ the error term.

>>>>

\subsection{Country boundaries}
To aggregate nighttime light intensity at the 30 arc-second cell level into the country level, we need the spatial data on country boundaries. 
We use GADM (2018), following Alesina et al.\ (2016) and Dreher et al.\ (2015) among others. 
The data include 256 countries and overseas territories. 
One country, Vatican, is dropped from the sample because it is smaller than the 30 arc-second cell. 
In addition, 75 countries and territories are also dropped from the sample as real GDP data is unavailable for all years from 1992 to 2013.
Excluding the three parent states of unrecognized states (Georgia, Azerbaijan, and Moldova), our base sample thus consists of 177 countries/territories in total.
\section{Methodology}
% Model of real GDP
We model real GDP in territory $i$ in year $t$, denoted by $y_{it}$, as follows:
\begin{equation}\label{gdp}
\ln(y_{it}) = \beta \ln(L_{it}) + \mu_i + \eta_t + \varepsilon_{it},
\end{equation}
where $L_{it}$ is nighttime light intensity in territory $i$ in year $t$, $\mu_i$ the territory fixed effect, $\eta_t$ the year fixed effect, and $\varepsilon_{it}$ the error term.
